A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-20 manuscript.Rmd
Update manuscript.Rmd

We have structured the tutorial with a _learning by doing_ approach in mind, such that readers can follow along at their own computers.
We explicitly encourage readers to try out all R commands for themselves.
Unless stated otherwise, all code blocks are meant to be run in the statistical programming language R (tested with version `r with(R.version, paste0(major, ".", minor))`).
To guide the reader through all steps of a research project, we will use a exemplary research question:

> "Is there a mean difference in the personality trait 'Machiavellism' between genders?"

This example serves only didactic purposes and not to derive substantive claims.
Nevertheless, everything else is kept as close to a real research question as possible and we have preregistered the analysis without looking at the data beforehand and use actual data subsequently.

@@

Such Monte-Carlo simulation can help you decide between several tradeoffs.
One historically important tradeoff is between sample size and power (the probability to detect an effect of given size).
More recently there has been growing interest in other resource relevant parameters as well [!citation], such as number of measurement occasions, reliability of measures etc.
To show that there can also be alternative approaches for sample size planning beyond null hypothesis testing, we choose to visualize the density distribution of the parameter of interest (latent mean difference by gender of Machiavellism) instead of power.
Such process still lets you formulate expectations for the precision of the analysis, e.g. with a sample size of 1000 per group 80% of the simulated standardized effect size fall into a range of +/- .1, but without necessarily rely on null hypothesis testing.
For simplicity we do not show the code for the simulation/graphic, but it is available in the accompanying [GitHub repository](https://github.com/aaronpeikert/repro-tutorial)[^gh-repo]:.

>>>>

We have structured the tutorial with a _learning by doing_ approach in mind, such that readers can follow along at their own computers.
We explicitly encourage readers to try out all R commands for themselves.
Unless stated otherwise, all code blocks are meant to be run in the statistical programming language R (tested with version `r with(R.version, paste0(major, ".", minor))`).

@@

Such Monte-Carlo simulation can help to decide between several trade-offs.
Historically, one important trade-off is between sample size and power (the probability to detect an effect of given size if it exists).
However, the question can be put more broadly and it is possible to consider various other trade-offs of relevant study design parameters other than sample size, such as number of measurement occasions [e.g., @brandmaier2015lifespan], reliability of measures [e.g., @brandmaier2018precision], or parameters related to the structure of planned-missing data design [@brandmaier2020optimal].
To show that there can also be alternative approaches for sample size planning other than those that are restricted to null hypothesis testing, we choose to visualize the precision of estimation as the density distribution of the parameter of interest (latent mean difference by gender of Machiavellism) instead of statistical power.
Such process still allow us to formulate expectations for the expected precision of the chosen analysis. For example, with a sample size of 1,000 per group, 80% of the simulated standardized effect sizes fall into a range of +/- .1 standardized difference points. This claim is useful and informative irrespective of whether we embark on null hypothesis testing later on or not.
The R code to reproduce the simulation and the figure can be found in the accompanying [GitHub repository](https://github.com/aaronpeikert/repro-tutorial)[^gh-repo]:.
